---
title: "Untitled"
author: "Vusi Mabasa"
date: "2022-11-24"
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(gtsummary)
library(caret)
```

###############################################SILVER########################################SILVER#########################################################################SILVER#################################################SILVER#######################################SILVER#########################################################################SILVER##################################################################################################################

```{r}
library(readxl)
Anzalysis_water <- read_excel("C:/Users/VUSI/Downloads/Anzalysis_water.xlsx", 
    range = "a2:e38")
```

```{r}
ModelA <- Anzalysis_water %>% select(Class, Nanomaterials, OD)
ModelA$Class <-as.factor(ModelA$Class)
```


```{r}
vus1 <- glm(Class ~ ., data = ModelA, family = binomial())
summary(vus1)
#vus1 %>% tbl_regression(exponentiate=T) %>% bold_p() %>% bold_labels() %>% add_significance_stars(hide_se = F, hide_p = F)
```

```{r}

set.seed(100)

TrainingIndex <- createDataPartition(ModelA[['Class']], p=0.8, list = FALSE)
Trainingset <- ModelA[TrainingIndex,]
Testingset <- ModelA[-TrainingIndex,]
```

```{r}

model <-train(Class ~.,data = Trainingset, method = "svmPoly",
              preProcess=c("scale", "center"), trControl= trainControl(method = "none"),
              tuneGrid= data.frame(degree=1 , scale=1, C=1))

```

```{r}
model.cv <- train(Class ~., data = Trainingset, method ="svmPoly",
                  preProcess = c("scale", "center"), trControl= trainControl(method = "cv",number = 10),
                  tuneGrid= data.frame(degree=1, scale=1, C=1))
```

#Apply mode for prediction
```{r}
model.training <- predict(model, Trainingset)
model.testing <- predict(model, Testingset)
model.cv <- predict(model.cv, Trainingset)
```

#model performance (display confusion matrix and statistics)
```{r}
model.training.confusion <- confusionMatrix(model.training, Trainingset[['Class']])
model.testing.confusion <- confusionMatrix(model.testing, Testingset[['Class']])
model.cv.confusion <- confusionMatrix(model.cv, Trainingset[['Class']])
```


# Print models
```{r}
print(model.training.confusion)
print(model.testing.confusion)
print(model.cv.confusion)
```




##FERIC-OXIDE##################################################FERIC-OXIDE####################FERIC-OXIDE#########################################################################
##FERIC-OXIDE###################################FERIC-OXIDE################################FERIC-OXIDE############################################################################
#######FERIC-OXIDE###################################################FERIC-OXIDE#######################################################################################


```{r}
library(readxl)
Anzalysis_water <- read_excel("C:/Users/VUSI/Downloads/Anzalysis_water.xlsx", 
    range = "g2:k38")
```

```{r}
ModelB <- Anzalysis_water %>% select(Class, OD, Nanomaterials)
ModelB$Class <-as.factor(ModelB$Class)
```

```{r}
ModelB <- data.frame(as.list(ModelB))
ModelB
```
```{r}
vus1 <- glm(Class ~ ., data = ModelB, family = binomial())
summary(vus1)
#vus1 %>% tbl_regression(exponentiate=T) %>% bold_p() %>% bold_labels() %>% add_significance_stars(hide_se = F, hide_p = F)
```

```{r}

set.seed(100)

TrainingIndex <- createDataPartition(ModelB[['Class']], p=0.8, list = FALSE)
Trainingset <- ModelB[TrainingIndex,]
Testingset <- ModelB[-TrainingIndex,]
```

```{r}

model <-train(Class ~.,data = Trainingset, method = "svmPoly",
              preProcess=c("scale", "center"), trControl= trainControl(method = "none"),
              tuneGrid= data.frame(degree=1 , scale=1, C=1))

```

```{r}
model.cv <- train(Class ~., data = Trainingset, method ="svmPoly",
                  preProcess = c("scale", "center"), trControl= trainControl(method = "cv",number = 10),
                  tuneGrid= data.frame(degree=1, scale=1, C=1))
```

#Apply mode for prediction
```{r}
model.training <- predict(model, Trainingset)
model.testing <- predict(model, Testingset)
model.cv <- predict(model.cv, Trainingset)
```

#model performance (display confusion matrix and statistics)
```{r}
model.training.confusion <- confusionMatrix(model.training, Trainingset[['Class']])
model.testing.confusion <- confusionMatrix(model.testing, Testingset[['Class']])
model.cv.confusion <- confusionMatrix(model.cv, Trainingset[['Class']])
```


# Print models
```{r}
print(model.training.confusion)
print(model.testing.confusion)
print(model.cv.confusion)
```


##############################################TITANIUM##############################TITANIUM#####################################################################
#################################################################################################################################################
################################TITANIUM################################TITANIUM#################################################################################

```{r}
library(readxl)
Anzalysis_water <- read_excel("C:/Users/VUSI/Downloads/Anzalysis_water.xlsx", 
    range = "m2:q38")
```

```{r}
ModelC <- Anzalysis_water %>% select(Class, Nanomaterials)
ModelC$Class <-as.factor(ModelC$Class)
```


```{r}
vus1 <- glm(Class ~ ., data = ModelC, family = binomial())
summary(vus1)
#vus1 %>% tbl_regression(exponentiate=T) %>% bold_p() %>% bold_labels() %>% add_significance_stars(hide_se = F, hide_p = F)
```


```{r}

set.seed(100)

TrainingIndex <- createDataPartition(ModelC[['Class']], p=0.8, list = FALSE)
Trainingset <- ModelC[TrainingIndex,]
Testingset <- ModelC[-TrainingIndex,]
```

```{r}

model <-train(Class ~.,data = Trainingset, method = "svmPoly",
              preProcess=c("scale", "center"), trControl= trainControl(method = "none"),
              tuneGrid= data.frame(degree=1 , scale=1, C=1))

```

```{r}
model.cv <- train(Class ~., data = Trainingset, method ="svmPoly",
                  preProcess = c("scale", "center"), trControl= trainControl(method = "cv",number = 10),
                  tuneGrid= data.frame(degree=1, scale=1, C=1))
```

#Apply mode for prediction
```{r}
model.training <- predict(model, Trainingset)
model.testing <- predict(model, Testingset)
model.cv <- predict(model.cv, Trainingset)
```

#model performance (display confusion matrix and statistics)
```{r}
model.training.confusion <- confusionMatrix(model.training, Trainingset[['Class']])
model.testing.confusion <- confusionMatrix(model.testing, Testingset[['Class']])
model.cv.confusion <- confusionMatrix(model.cv, Trainingset[['Class']])
```


# Print models
```{r}
print(model.training.confusion)
print(model.testing.confusion)
print(model.cv.confusion)
```
